An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-09-23 latex_files/ch3/3_1_ELFI.tex
create tikz figures and plots
fixed warnings
light edits in ELFI section

\pkg{Engine for Likelihood-Free Inference (ELFI)}\footnote{Extended
  documentation can be found
  \href{https://elfi.readthedocs.io/en/latest/}{here}}~\cite{1708.00707}
is a \proglang{Python} package dedicated to Likelihood-Free Inference
(LFI). We implemented ROMC at \pkg{ELFI} since it provides convenient
modules for all the fundamental components of a probabilistic model
(e.g. prior, simulator, summaries etc.). Furthermore, \pkg{ELFI}
already supports some recently proposed likelihood-free inference
methods, making it straightforward to perform comparisons between
methods. The implementation was officially added to \pkg{ELFI} at
version \pkg{v0.8.0}.

@@

\pkg{ELFI} models the probabilistic model as a Directed Acyclic Graph
(DAG). This functionality is based on the package \pkg{NetworkX},
which supports general-purpose graphs. In most cases, the structure of
a likelihood-free model follows the pattern of figure~\ref{fig:elfi};
some edges connect the prior distributions to the simulator, the
simulator is connected to the summary statistics that, in turn, lead
to the output node. Samples can be obtained from all nodes through
sequential sampling. \pkg{ELFI} automatically considers as parameters
of interest, i.e. those we try to infer a posterior distribution,
as the ones  defined through the \code{elfi.Prior} class. Finally, the
observations are passed to the appropriate node through the argument
\code{observed}.

\begin{figure}[h]
    \begin{center}
      \includegraphics[width=0.8\textwidth]{./latex_files/images/chapter2/elfi.png}
    \end{center}
    \caption[Baseline example for creating an \pkg{ELFI} model]{Baseline example for creating an \pkg{ELFI} model. Image taken from \cite{1708.00707}}
    \label{fig:elfi}
\end{figure}

@@

All inference methods at \pkg{ELFI} share the following rules;

>>>>

\pkg{Engine for Likelihood-Free Inference (ELFI)}\footnote{Extended
  documentation can be found
  \href{https://elfi.readthedocs.io/en/latest/}{here}}~\cite{1708.00707}
is a \proglang{Python} package for Likelihood-Free Inference
(LFI). We selected to implemented ROMC in \pkg{ELFI} since it provides
convenient modules for all the fundamental components of a
probabilistic model (e.g.\ prior, simulator, summaries
etc.). Furthermore, \pkg{ELFI} already supports some recently proposed
likelihood-free inference methods, making it straightforward to
perform comparisons between methods. The implementation was officially
added to \pkg{ELFI} in version \pkg{v0.8.0}.

@@

\pkg{ELFI} models the probabilistic model as a Directed Acyclic Graph
(DAG). This functionality is based on the package \pkg{NetworkX},
which supports general-purpose graphs. In most cases, the structure of
a likelihood-free model follows the pattern of figure~\ref{fig:elfi};
some edges connect the prior distributions to the simulator, the
simulator is connected to the summary statistics that, in turn, lead
to the output node. Samples can be obtained from all nodes through
sequential (ancestral) sampling. \pkg{ELFI} automatically considers as
parameters of interest, i.e. those we try to infer a posterior
distribution, as the ones defined through the \code{elfi.Prior}
class. Finally, the observations are passed to the appropriate node
through the argument
\code{observed}.

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.8\textwidth]{./latex_files/images/chapter2/elfi.png}
    \end{center}
    \caption[Baseline example for creating an \pkg{ELFI} model]{Baseline example for creating an \pkg{ELFI} model. Image taken from \cite{1708.00707}}
    \label{fig:elfi}
\end{figure}

@@

All inference methods in \pkg{ELFI} share the following rules;
